Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-02-01 paper/paper.tex
described algorithm

The prediction problem at hand is a multiclass classification. We choose to
attack this using one-vs-rest scheme on a binary logistic regression, whose
loss can be written as
\[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, w\rangle)) + \lambda\Omega(w),\]
if \(y\in{-1, 1}\) and with \(x_i\in\R^p\) the training sample brain images.

\paragraph{Optimization.}
We optimize the data loss function using an iterative forward-backward
scheme analogous to (F)ISTA for the lasso \cite{beck2009}. We divide the
loss \(\mathcal L(w)\) into a smooth, convex data fit term \(F(w)\) (here: 
logistic regression loss) and a potentially non-smooth, convex 
regularization term

>>>>

The prediction problem at hand is a multiclass classification. We choose to
attack this using one-vs-rest scheme on a binary logistic regression, whose
loss can be written as
\[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, w\rangle)) + \lambda\Omega(w),\]
if \(y\in\{-1, 1\}\) and with \(x_i\in\R^p\) the training sample brain images.

\paragraph{Optimization.}
We optimize the data loss function using an iterative forward-backward
scheme analogous to (F)ISTA for the lasso \cite{beck2009}. 
{\color{red} Michael: Algorithm specification to be removed for ICML - supposed known, except possibly for hierarchical prox.}
We divide the
loss \(\mathcal L(w)\) into a smooth, convex data fit term \(F(w)\) (here: 
logistic regression loss) and a potentially non-smooth, convex 
regularization term \(G(w)\). 
Define \(\prox_{\gamma G}(v) = (\Id + \gamma\partial G)^{-1}(v)\), where \(\partial G\) is the subdifferential of \(G\) and 
let \(\nabla F(v)\) be the gradient of \(F\) in \(v\). Further let \(L > 0\)
be a Lipschitz constant of the gradient of \(F\) and choose a step size
\(\varepsilon\in (0, \frac{2}{L})\). Starting with an arbitrary 
initialization of \(w_0\), putting \(z_1 = w_0\) and \(t_1 = 1\), then for
\(k\geq 1\) until convergence do:
\begin{eqnarray*}
  x_k & = & \prox_{\varepsilon G}(y_k - \varepsilon\nabla F(y_k))\\
  t_{k + 1} & = & \frac{1 + \sqrt{1 + 4 t_k^2}}{2}\\
  y_{k + 1} & = & x_k + \left(\frac{t_k - 1}{t_{k + 1}}\right)(x_k - x_{k - 1})
\end{eqnarray*}
In our case \(G(v) = \lambda\Omega(v)\). Splitting \(\Omega(v) = \Omega_{\mathcal H}(v) + \Omega_{\mathcal G}(v)\) with 
\(\Omega_{\mathcal H}(v) = \alpha\sum_{h\in\mathcal H}\eta_h\|v_h\|_2\) and
\(\Omega_{\mathcal G}(v) = \beta\sum_{g\in\mathcal G}\eta_g\|v_g\|_2\), we observe
that \[\prox_{\varepsilon\lambda\Omega_{\mathcal H}}(v) = \sum_{h\in\mathcal H}\iota_h\left([\|v_h\|_2 > \eta_h\varepsilon\lambda\alpha]\left(v_h - \eta_h\varepsilon\lambda\alpha\frac{v_h}{\|v_h\|_2}\right)\right),\]
where \(\iota_h\) is the canonical injection of the group \(h\) into 
\(\R^p\) (if \(\pi_g: v\mapsto v_g\), then \(\iota_g = \pi_g^\ast\) the 
adjoint/transposed operator). This holds analogously for 
\(\Omega_{\mathcal G}\).
According to \cite{jenatton2011}, the proximal operator of 
the hierarchical penalty \(\varepsilon\lambda\Omega\) is
\[\prox_{\varepsilon\lambda\Omega}(v) = \prox_{\varepsilon\lambda\Omega_{\mathcal H}}\circ\prox_{\varepsilon\lambda\Omega_{\mathcal G}}(v).\]
